# Tinyverse {#tinyverse}

## Get recursive dependencies

### CRAN

List recursive dependencies of ggplot2, for example. This should be all
the packages that will be installed when one attempts to install ggplot2
in a fresh R installation (v4.0.0 in this case).

```{r}
library(miniCRAN)
```

```{r}
# Get vector of recursive dependencies in alphabetical order
sort(
  miniCRAN::pkgDep(
    "ggplot2", 
    depends = TRUE, 
    suggests = FALSE, 
    enhances = FALSE, 
    includeBasePkgs = TRUE, 
    Rversion = "4.0.0"
  )
)
```

Make a graph of these dependencies.

```{r}
# Make dependency graph
dg <- miniCRAN::makeDepGraph(
  "ggplot2", 
  depends = TRUE, 
  suggests = FALSE, 
  enhances = FALSE, 
  includeBasePkgs = TRUE, 
  Rversion = "4.0.0"
)
set.seed(1)
plot(dg, legendPosition = c(-1, -1), vertex.size = 10, cex = 0.7)
```

### Bioconductor

List recursive dependencies of affy, for example. This should be all
the packages that will be installed when one attempts to install affy
in a fresh R installation (v4.0.0 in this case).

```{r}
# Get matrix of all Bioconductor packages and their URLs
library(BiocManager)
```

```{r}
biocUrl <- repositories()["BioCsoft"]

index <- function(url, type="source", filters=NULL){
  contribUrl <- contrib.url(url, type=type)
  available.packages(contribUrl, type=type, filters=filters)
}

biocIndex <-index(biocUrl)

# Get vector of recursive dependencies
sort(
  miniCRAN::pkgDep(
    "affy",
    availPkgs = biocIndex,
    repos = biocIndex[,"Repository"],
    depends = TRUE,
    suggests = FALSE,
    enhances = FALSE,
    includeBasePkgs = TRUE,
    Rversion = "4.0.0"
  )
)
```

Make a graph of these dependencies.

```{r}
# Make dependency graph
dg <- miniCRAN::makeDepGraph(
  "affy",
  availPkgs = biocIndex,
  repos = biocIndex[, "Packages"],
  depends = TRUE, 
  suggests = FALSE, 
  enhances = FALSE, 
  includeBasePkgs = TRUE, 
  Rversion = "4.0.0"
)

set.seed(1)
plot(dg, legendPosition = c(-1, -1), vertex.size = 10, cex = 0.7)
```

